\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[purple]{classic}
% CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and
% 'banking'
% CV color - options include: 'blue' (default), 'orange', 'green', 'red',
% 'purple', 'grey' and 'black'
\usepackage[top=1cm, bottom=1cm, left=1cm, right=1cm]{geometry}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{multibib}
\usepackage{fontawesome5}
\usepackage{multido}

\firstname{
  Pierre
}
\familyname{
  Sassoulas
}
\title{
  Software engineer, Open-source maintainer
}
\email{
  pierre.sassoulas at gmail.com
}
\social[github]{pierre-sassoulas}
\social[linkedin]{pierresassoulas}

\input{address}
\input{mobile_phone}

%\extrainfo{
%  Current Clean Driving Licence
%} % \\ et du CACES nacelle}
% CACES Valide uniquement entre 2008 et 2013 (Valable 5 ans)

%\photo[92pt][0.4pt]{picture.jpg}

\nopagenumbers{}

\begin{document}
  \maketitle
  \vspace*{-3mm}

  \section{PROFESSIONAL SUMMARY}\label{sec:summary}
  \cvline{}{
      Software engineer with a generalist scientific background with 10+ years of professional experience in web
      development and DevOps (often in startups), and open-source leadership. Extensive background in full-stack
      development, site reliability engineering, solar energy, and mentoring. Core maintainer of Pylint and Pytest,
      two packages used respectively by 15\% and 50\% of python developers (according to JetBrain's survey).
  }

  \vspace{5mm}

  \section{KEY PROFESSIONAL EXPERIENCE}
  \label{sec:key-professional-experience}

  \cventry
    {\textbf{SRE} \textbf{management} \textbf{Orchestration}}
    {DevOps Engineer => DevOps Team Lead}
    {Elum Energy}
    {Remote}
    {September 2022 - present}{
    \begin{itemize}
        \item \textbf{DevOps Team Lead (February 2025 - present):} Expanded role beyond DevOps engineering to include team management,
        organization, and annual performance evaluations.
        \item \textbf{DevOps Engineer (September 2022 - January 2025):}  Delivered training, designed tools,
            and implemented practices that accelerate our ability to deliver products at scale, from
            automated hardware provisioning to remote fleet management, and monitoring of our energy management
		    systems (EMS). Manage our in-house infrastructure (on-premises and in Scaleway/GCP/AWS),
            and provide L3 support by troubleshooting complex issues that go beyond the scope of our support team.
    \end{itemize}
    }

    \cventry
    {\textbf{Product management}}
    {Core Maintainer}
    {Open-source}
    {GitHub}
    {November 2016 - present}{
      \begin{itemize}
          \item \textbf{pytest (December 2022 - present):} Testing framework for Python, used by 50\% of Python developers.
          \item \textbf{prospector (August 2021 - present):} Code quality tool for Python, integrating multiple analysis tools, with
            400k+ installations per month from Pypi.
          \item \textbf{pylint (November 2016 - present):} Static code analysis tool based on the python ast
            rebuilt and augmented in \textbf{astroid}, used by 15\% of Python developers.
      \end{itemize}
    }

    \cventry
    {\textbf{Business ownership}}
    {Freelance}
    {Self employed}
    {Remote}
    {January 2020 - present}{
        Deliver technical expertise and advisory services to corporate and academic partners
        (e.g., Yale, MIT, Tidelift, and others under NDA) in the context of my maintained
        open-source repositories, encompassing feature implementation, giving supply chain
        security guarantees, and AI output evaluation.
    }

  \cventry
    {\textbf{mentorship} \textbf{change management}}
    {Technical Lead}
    {EdF Store \& Forecast}
    {Lyon}
    {July 2020 - February 2022}{
      Within the 15 persons optimization \& Forecasting team, setting up packaging and an
      internal python package server, testing, automatic commit level checks
      through static analysis, continuous integration, dockerization, and
      continuous production deployment using ansible and kubernetes. Provided
      training on software topics and proposed solutions for the harmonization,
      design, and maintainability of software products.
    }

  \vspace{5mm}

  \section{EDUCATION}\label{sec:education}
  \cventry
    {2009 - 2015}
    {Master's Degree in Engineering}
    {INSA de Rouen}
    {3 years CS/IT specialization following 2 years of generalist studies
        (math, physics, chemistry, mechanics, electronics, communication)}
	{}{}

%  \cventry
%    {2009}
%    {BAC S mention BIEN}
%    {Lycée Alain Borne}
%    {Option biologie}
%    {Montélimar}
%    {}

%  \cventry
%    {2008}
%    {Caces Nacelle}
%    {CEFTIC de Pierrelatte}
%    {}{}{}

    \section{LANGUAGE}\label{sec:language}

  \cvlanguage
    {French}
    {Native}{}{}{}{}

  \cvlanguage
    {English}
    {Advanced (C2) (TOEIC 2013: 920/990)}
    {Volunteer translator for Ubuntu, Jenkins and FlossManual}

  \cvlanguage
    {Spanish}
    {Intermediate}
    {}{}{}{}

  \section{COMPUTING SKILLS}\label{sec:computing-skills}

  \cvcomputer
    {\textbf{Languages}}
    {Python, Bash, C/C++, SQL, Lua, C\#}
    {\textbf{Tools}}
    {Git, Docker, pre-commit, Sphinx, Plantuml}

  \cvcomputer
    {\textbf{Frameworks}}
    {Django, Bootstrap, Slack SDK, Unity}
    {\textbf{Software}}
    {Gimp, Inkscape, Audacity, Adobe Suite}

  \cvcomputer
    {\textbf{DevOps}}
    {Continuous Deployment, Apache, Ansible, Kubernetes, SaltStack}
    {\textbf{Office software}}
    {\LaTeX{}, C2I 2mi (LibreOffice, Office)}

  \newpage

    \section{COMPLETE PROFESSIONAL HISTORY}\label{sec:complete-professional-history}

  \cventry
    {\textbf{client-focus} \textbf{pragmatism}}
    {Technical Consultant / Software Engineer}
    {Antidot}
    {Lyon}
    {September 2018 - July 2020}{
        Development of specific modules; level 3 support and management of a deployment pipeline
        of a technical documentation platform or document search and processing solutions. Implementation
        of standards and tools within a newly created team. Converted document
        formats (Word, Framemaker, etc.) to HTML. Made an internal API usable by external integrators.
    }

  \cventry
    {\textbf{C++} \textbf{docker} \textbf{python}}
    {Software Engineer}
    {WiseBim}
    {Remote work}
    {January 2018 - July 2018}{
      Set up of a SAAS architecture allowing to automatically generate 3D
	  building information modeling (BIM) based on architectural 2D plans in
	  a secure and reliable manner through a web interface.
    }

  \cventry
    {\textbf{big data} \textbf{python} \textbf{C++}}
    {Research Engineer}
    {CEA/INES}
    {Chambéry}
    {June 2016 to December 2017 (Fixed contract)}{
      Study and implementation of a database cluster and its web interface in
      order to store, display and analyse a wide variety of data flux stemming
      from sensors.
    }

  \cventry
    {\textbf{ruby} \\ \textbf{XML} \textbf{DO178}}
    {Software Engineering Intern}
    {Thales Avionics SAS}
    {Valence (France)}
    {6 months}{
      Specification, design, development, and qualification according to
      the DO330 norm of a quality tool for avionics software development.
    }

  \cventry
    {\textbf{python} \textbf{SQL} \textbf{web}}
    {Project leader and developer}
    {A2IA, INSA}
    {Rouen}
    {2 semesters }{
      Project management and development of a tool managing big volume of
      metadata for character recognition. During 25 hours a week in a group of
      15 INSA students following the ISO9001:2008 norm.
    }

  \cventry
    {\textbf{python} \textbf{SOAP} \textbf{Quality}}
    {Developer}
    {Dynamease, INSA}
    {Rouen}
    {1 semester }{
       Development of an openERP module for phone call management. During
       25 hours a week in a group of 7 INSA students respecting the
       ISO9001:2008 norm.
    }

  \cventry
    {\textbf{python} \textbf{web}}
    {Software Engineering Intern}
    {Bull}
    {Grenoble}
    {3 months}{
      Development of a quotation tool easing the choice and buying procedure
      of supercomputer parts.
    }

%  \cventry
%    {\textbf{monde du travail}}
%    {Stage ouvrier}
%    {Autajon}
%    {Montélimar}
%    {9 semaines}{
%      Remise à jour et réorganisation des stocks d'outillage de l'atelier
%      découpe.
%    }

%  \cventry
%    {\textbf{monde du travail}}
%    {Agent d'entretien en contrat saisonnier}
%    {ASF, Autajon}
%    {Montélimar}
%    {2 étés}{
%      Nettoyage de toilettes d'autoroutes, nettoyage en hauteur à l'aide d'une
%      nacelle.
%    }

%  \cventry
%    {\textbf{HTML} \textbf{css} \textbf{js}}
%    {Middle school student}
%    {Middle school}
%    {Montélimar}
%    {October 2004 - June 2005}{
%        Creating and maintaining HTML websites including the intranet and the
%        internet site of my middle school.
%    }

%  \cventry
%    {\textbf{monde du travail} \textbf{Rédaction}}
%    {Stage de troisième}
%    {La tribune}
%    {Montélimar}
%    {Une semaine}{
%      Rédaction d'article, mise en page, critique de livre, « reportage » au
%      tournoi UNSS départemental de handball.
%    }

  \vspace{5mm}

  \section{PERSONAL PROJECTS \& COMMUNITY}\label{sec:personal-experience}

    \cventry
    {\textbf{mentorship}, \textbf{pedagogy}}
    {Computer working group facilitator}
    {Mixteen}
    {Lyon}
    {May 2019 - present}{
	  Supervising children during workshop that allow children to discover computer science in a
	  playful manner with tools like Scratch, Thymio, Pygame and Micro$:$bit depending on their age,
      at conferences like Mixit or pyconfr.
    }

    \cventry
    {\textbf{open-source}}
    {Author or Maintainer}
    {Open-source}
    {GitHub / Wikipedia}
    {March 2006 - present}{
          \begin{itemize}
%          \item \textbf{pydocstringformatter (December 2022 - present):} Tool to autoformat python docstrings,
%            with 15k+ installation per month from Pypi.
          \item \textbf{grey-handling (August 2019 - present):} World of Warcraft addon
            to manage grey items with group communications, with 10k+ installation from CurseForge.
          \item \textbf{django-zxcvbn-password-validator (June 2018 - present):} Translated Django password
            validator based on Dropbox's zxcvbn library, with 75k+ installation per month from Pypi.
          \item \textbf{pySankeybeta (October 2017 - present):} Library to generate Sankey diagrams, with
            2k+ installation per month from Pypi (1k+ coming from django-survey-and-report).
          \item \textbf{django-survey-and-report (June 2017 - present):} Survey app for Django,
            allowing to easily create and manage surveys, with 1k+ installation per month from Pypi.
          \item \textbf{possum (January 2011 - August 2016):} A point of sales for bar used by 20 bar owner in the
            Rouen region until a stricter point of sale legislation killed the project in 2018.
%          \item \textbf{Wikipedia (March 2006 - present):} Contributed to various niche topics.
      \end{itemize}
    }

      \cvline
    {\textbf{game design}}
    {
      Design, development and team coordination around a 3D chess game with a twist in the historical
      setting of the French revolution named \href{https://discord.gg/jSZGdWYXHY}{Revenge of the Pawns \faDiscord} (in progress).
    }{}{}

    \cventry
    {\textbf{Film making}}
    {Factotum}
    {Insa}
    {Rouen}
    {February 2010 - June 2014}{
      In groups of 3 to 5, writing, filming, editing and promoting of a
      feminist comedy, an action film, a suspens film and a modern western as
      part of the ``Section Image Étude'' in INSA.
    }

%  \cvline
%    {\textbf{python}, \textbf{web}}
%    {
%      Refactoring of INSA's ``Mission qualité'' website
%      (permitting to realize statistics and survey about the satisfaction of
%      student and employees each semester).
%    }{}{}

  \cvline
    {\textbf{electronic}, \textbf{arduino}}
    {
      Design and development of an arduino controlled wood cube allowing
      to play tic tac toe with an integrated keyboard and 9 tricolored LEDs.
    }{}{}

    \cvline
    {\textbf{C}, \textbf{\LaTeX{}}}{
      Design and development of the artificial intelligence of an othello
      software and of an othello tournament manager.
    }

  \cvline
    {\textbf{C++}, \textbf{matlab}}
    {
      Design and development of a profiling module for the free software
      Teeworld.
    }{}{}

\end{document}
